MIGRACE DAT - DEMUS / MUSEION

### 2023-02-13 R_BIOLIB_slovniky.Rmd
BioLib - Animalia DONE

path <-  "C:/Users/krizova/Documents/R_migrace/"

@@

ani1 <- merge(kmen, trida, by.x = "kmen_Nomen", by.y = "trida_NadNomen", all.y = T)
ani2 <- merge(ani1, rad, by.x = "trida_Nomen", by.y = "rad_NadNomen", all.y = T)
ani3 <- merge(ani2, celed, by.x = "rad_Nomen", by.y = "celed_NadNomen", all.y = T)
ani4 <- merge(ani3, rod, by.x = "celed_Nomen", by.y = "rod_NadNomen", all.y = T)
ani5 <- merge(ani4, druh, by.x = "rod_Nomen", by.y = "druh_NadNomen", all.y = T)
ani6 <- merge(ani5, poddruh, by.x = "druh_Nomen", by.y = "poddruh_NadNomen", all = T)

@@

rm(ani1)
rm(ani2)
rm(ani3)
rm(ani4)
rm(ani5)
```

>>>>

path <-  "C:/Users/krizova/Documents/R/"

@@

# ani1 <- merge(kmen, trida, by.x = "kmen_Nomen", by.y = "trida_NadNomen", all.y = T) # 98
# ani2 <- merge(ani1, rad, by.x = "trida_Nomen", by.y = "rad_NadNomen", all.y = T) # 581
# ani3 <- merge(ani2, celed, by.x = "rad_Nomen", by.y = "celed_NadNomen", all.y = T) # 6 515
# ani4 <- merge(ani3, rod, by.x = "celed_Nomen", by.y = "rod_NadNomen", all.y = T) # 19 643
# ani5 <- merge(ani4, druh, by.x = "rod_Nomen", by.y = "druh_NadNomen", all.y = T) # 103 970
# ani6 <- merge(ani5, poddruh, by.x = "druh_Nomen", by.y = "poddruh_NadNomen", all = T) # 124 505

# inner_join - wrong path

# ani1 <- inner_join(kmen, trida, by = c("kmen_Nomen" = "trida_NadNomen")) # 98
# ani2 <- inner_join(ani1, rad, by = c("trida_Nomen" = "rad_NadNomen")) # 557
# ani3 <- inner_join(ani2, celed, by = c("rad_Nomen" = "celed_NadNomen")) # 6 153
# ani4 <- inner_join(ani3, rod, by = c("celed_Nomen" = "rod_NadNomen")) # 18 324
# ani5 <- inner_join(ani4, druh,by = c("rod_Nomen" = "druh_NadNomen")) # 92 791
# ani6 <- inner_join(ani5, poddruh, by = c("druh_Nomen" = "poddruh_NadNomen")) # 25 972

# right_join - this setup gives exactely the same result as 'merge', BUT WITH ORDERED COLUMNS

# ani11 <- right_join(kmen, trida, by = c("kmen_Nomen" = "trida_NadNomen"), keep = T) # 98
# ani22 <- right_join(ani1, rad, by = c("trida_Nomen" = "rad_NadNomen"), keep = T) # 557
# ani33 <- right_join(ani2, celed, by = c("rad_Nomen" = "celed_NadNomen"), keep = T) # 6 153
# ani44 <- right_join(ani3, rod, by = c("celed_Nomen" = "rod_NadNomen"), keep = T) # 18 324
# ani55 <- right_join(ani4, druh,by = c("rod_Nomen" = "druh_NadNomen"), keep = T) # 92 791
# ani66 <- left_join(ani5, poddruh, by = c("druh_Nomen" = "poddruh_NadNomen"), keep = T) # 25 972

# full_join - this setup gives full table WITH ALL and ORDERED COLUMNS

join1 <- full_join(kmen, trida, by = c("kmen_Nomen" = "trida_NadNomen"), keep = T, multiple = "any") # 111
join2 <- full_join(join1, rad, by = c("trida_Nomen" = "rad_NadNomen"), keep = T, multiple = "any") # 605
join3 <- full_join(join2, celed, by = c("rad_Nomen" = "celed_NadNomen"), keep = T, multiple = "any") # 6 569
join4 <- full_join(join3, rod, by = c("celed_Nomen" = "rod_NadNomen"), keep = T, multiple = "any") # 23 970
join5 <- full_join(join4, druh,by = c("rod_Nomen" = "druh_NadNomen"), keep = T, multiple = "any") # 108 313
join6 <- full_join(join5, poddruh, by = c("druh_Nomen" = "poddruh_NadNomen"), keep = T, multiple = "any") # 128 848

#   p  i  s  k  o  v  i  s  t  e  -  ZACATEK

check_kt <- join6 %>% 
  select(kmen_Nomen, trida_NadNomen, trida_Nomen) %>% 
  distinct()

check_tr <- join6 %>% 
  select(trida_Nomen, rad_NadNomen, rad_Nomen) %>% 
  distinct() %>% 
  filter(is.na(trida_Nomen))

check_rc <- join6 %>% 
  select(rad_Nomen, celed_NadNomen, celed_Nomen) %>% 
  distinct() %>% 
  filter(is.na(rad_Nomen))

write.table(check_rc, paste0(path_csv, "check_tabs2print_rc.csv"), sep = ";", row.names = F)

check_tab <- join6 %>% 
  select(kmen_Nomen, trida_NadNomen, trida_Nomen, 
         rad_NadNomen, rad_Nomen, 
         celed_NadNomen, celed_Nomen, 
         rod_NadNomen, rod_Nomen, 
         druh_NadNomen, druh_Nomen, 
         poddruh_NadNomen, poddruh_Nomen, 
         )

check_tab2 <- check_tab %>% 
  select(-poddruh_Nomen, -poddruh_NadNomen, -druh_Nomen) %>% 
  filter(is.na(kmen_Nomen)) %>% 
  distinct()

# write.table(check_tab2, paste0(path_csv, "check_kmeny.csv"), sep = ";")

check_kmen <- check_tab %>% 
  select(kmen_Nomen, trida_NadNomen) %>% 
  distinct() %>% 
  filter(is.na(trida_NadNomen))

check_trida <- check_tab %>% 
  select(trida_Nomen, rad_NadNomen) %>% 
  distinct() 
  filter(is.na(rad_NadNomen))

check_chordata <- join6 %>% 
  filter(rad_NadNomen %in% c("Chordata"))

#   p  i  s  k  o  v  i  s  t  e  -  KONEC

@@

rm(ani1)
rm(ani2)
rm(ani3)
rm(ani4)
rm(ani5)
